\bf Causal Inference in Population Trends: Searching for Demographic Anomalies in Big Data

### 2020-01-24 MANUSCRIPT/manuscript.Rmd
Typo corrections.

We report outliers using a simple t-statistic and report the size of the outlier, or its impact on the time series, by subtracting $\hat{y}$, the adjusted time series without outliers removed, from $y$, the original, unadjusted time series.

>>>>

We report outliers using a simple t-statistic and report the size of the outlier, or its impact on the time series, by subtracting $\hat{y}$, the adjusted time series with outliers removed, from $y$, the original, unadjusted time series.

### 2020-01-24 MANUSCRIPT/manuscript.tex
Typo corrections.

We report outliers using a simple t-statistic and report the size of the
outlier, or its impact on the time series, by subtracting \(\hat{y}\),
the adjusted time series without outliers removed, from \(y\), the
original, unadjusted time series.

>>>>

We report outliers using a simple t-statistic and report the size of the
outlier, or its impact on the time series, by subtracting \(\hat{y}\),
the adjusted time series with outliers removed, from \(y\), the
original, unadjusted time series.
